Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-10-21 paper/ms.tex
Add period.

{\color{blue} 
The evolution of the fraction, by mass, of IGE material expected to be in the form of \Ni{56} after 
freeze-out is shown in Figure \ref{fig:compare_ratio}. The figure presents the results from the
same realizations as in Figure \ref{fig:nithybrid} The ratios for the yields of 
explosions from hybrid progenitors are consistently lower than the ratios of yields from
traditional progenitors.
Figure~\ref{fig:compare_burned} shows the 
concurrent evolution of mass burned to IGE for realizations 25-30 from both suites.
The total IGE has a mostly similar evolution, and the hybrid results show
more scatter, but there is not an obvious difference between the results from
the two progenitors. These plots together show that the 
ratio is the quantity that demonstrates important differences between 
C-O and C-O-Ne cases.
}

>>>>

{\color{blue} 
The evolution of the fraction, by mass, of IGE material expected to be in the form of \Ni{56} after 
freeze-out is shown in Figure \ref{fig:compare_ratio}. The figure presents the results from the
same realizations as in Figure \ref{fig:nithybrid}. The ratios for the yields of 
explosions from hybrid progenitors are consistently lower than the ratios of yields from
traditional progenitors.
Figure~\ref{fig:compare_burned} shows the 
concurrent evolution of mass burned to IGE for realizations 25-30 from both suites.
The total IGE has a mostly similar evolution, and the hybrid results show
more scatter, but there is not an obvious difference between the results from
the two progenitors. These plots together show that the 
ratio is the quantity that demonstrates important differences between 
C-O and C-O-Ne cases.
}
